BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-06 tex/3-algorithms.tex
up

% textual pseudocode
Algorithm \ref{extractionAlgo} show the generic procedure we use to build extraction rules. The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all possible extraction rules the best one with respect to a certain \code{ScoreFunction}. The rule which is most frequently a \emph{best rule} is then returned.

@@

% embarrassingly parallel
One might notice that each \emph{best rule} computation is independent and operates on a different input pairs. This implies that Algorithm \ref{extractionAlgo} is \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed on multiple threads.

% abs, plan
Functions in Algorithm \ref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section. \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction. In \ref{timecomplexityandlinearreformulation} we analyses time complexity of Algorithm \ref{extractionAlgo} and give a linear time reformulation using dynamic programing. Finally, \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.

@@

% xpath selectors (id, else class, else path)
In our implementation, rules are queries in the XML Path Language (XPath). Consequently, standard libraries can be used to parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in Algorithm \ref{extractionAlgo}. We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree. \code{id} attributes are expected to be unique, and \code{class} attributes have showed to have better consistency than absolute paths over pages of a blog. For these reasons, the \coderef{allrulesAlgo} function returns a single rule per node:

@@

Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article. Table \ref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.

@@

% into: algo 1 defined
With functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) defined, the definition of Algorithm \ref{extractionAlgo} for article extraction is completed. We now proceed with a time complexity analysis.

@@

% linear reformulation
We now present Algorithm \ref{linearAlgo}, a linear time reformulation of Algorithm \ref{extractionAlgo} for article extraction using dynamic programming. While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from effectively reusing previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement \emph{memoization} over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree and computes node bigrams from their children bigrams. This way, we avoid serializing HTML subtrees for each bigrams computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.

@@

% proof
With bigrams computed in this dynamic programming manner, the total time needed to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear. To conclude the proof that Algorithm \ref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time. As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigrams unions per inner loop iteration tends to one. Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams length computations. Over a finite alphabet (we used printable ASCII), bigrams sizes have bounded size and each of these operations takes constant time.

@@

% comments
Comments are usually available in separate web feeds, one per blog post. Similarly to blog feeds, comment feeds have a limited number of entries, and when the number of comments on a blog post exceeds this limit, comments have to be extracted from the post web page. To do so we use the following \code{ScoreFunction}:
\begin{itemize}
  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
\end{itemize}
Our crawler executes this algorithm on each post with overflow on its comment feed, thus supporting blogs with multiple commenting engines. Comment contents are extracted first, which allows to narrow down the initial filtering by fixing a target number of comments.

% rush some time complexity analysis
Regarding time complexity, computing the \emph{tree distance} of each nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affects the asymptotic computational complexity. While scoring rules for comments extraction requires a more expensive algorithm, the proportion of candidates left after filter out rules with an insufficient number of results is very low in practice. Analog reformulations to the one done with Algorithm \ref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

>>>>

% textual pseudocode
\autoref{extractionAlgo} show the generic procedure we use to build extraction rules. The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all possible extraction rules the best one with respect to a certain \code{ScoreFunction}. The rule which is most frequently a \emph{best rule} is then returned.

@@

% embarrassingly parallel
One might notice that each \emph{best rule} computation is independent and operates on a different input pairs. This implies that \autoref{extractionAlgo} is \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed on multiple threads.

% abs, plan
Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section. \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction. In \ref{timecomplexityandlinearreformulation} we analyses time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programing. Finally, \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.

@@

% xpath selectors (id, else class, else path)
In our implementation, rules are queries in the XML Path Language (XPath). Consequently, standard libraries can be used to parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in \autoref{extractionAlgo}. We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree. \code{id} attributes are expected to be unique, and \code{class} attributes have showed to have better consistency than absolute paths over pages of a blog. For these reasons, the \coderef{allrulesAlgo} function returns a single rule per node:

@@

Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article. \autoref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.

@@

% into: algo 1 defined
With functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) defined, the definition of \autoref{extractionAlgo} for article extraction is completed. We now proceed with a time complexity analysis.

@@

% linear reformulation
We now present \autoref{linearAlgo}, a linear time reformulation of \autoref{extractionAlgo} for article extraction using dynamic programming. While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from effectively reusing previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, \autoref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement \emph{memoization} over the bigrams computations, \autoref{linearAlgo} uses a post-order traversal of the HTML tree and computes node bigrams from their children bigrams. This way, we avoid serializing HTML subtrees for each bigrams computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.

@@

% proof
With bigrams computed in this dynamic programming manner, the total time needed to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear. To conclude the proof that \autoref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time. As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigrams unions per inner loop iteration tends to one. Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams length computations. Over a finite alphabet (we used printable ASCII), bigrams sizes have bounded size and each of these operations takes constant time.

@@

% comments
Comments are usually available in separate web feeds, one per blog post. Similarly to blog feeds, comment feeds have a limited number of entries, and when the number of comments on a blog post exceeds this limit, comments have to be extracted from the post web page. To do so we use the following \code{ScoreFunction}:
\begin{itemize}
  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
\end{itemize}
Our crawler executes this algorithm on each post with overflow on its comment feed, thus supporting blogs with multiple commenting engines. Comment contents are extracted first, which allows to narrow down the initial filtering by fixing a target number of comments.

% rush some time complexity analysis
Regarding time complexity, computing the \emph{tree distance} of each nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affects the asymptotic computational complexity. While scoring rules for comments extraction requires a more expensive algorithm, the proportion of candidates left after filter out rules with an insufficient number of results is very low in practice. Analog reformulations to the one done with \autoref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

### 2013-12-06 tex/5-evaluation.tex
up

Our evaluation will be articulated in two parts. Firstly, we will compare the article extraction procedure presented in section \ref{algorithms} with three open source projects capable of extracting content and title of web articles. The comparison will show that our blog targeted solution has better performances both in term of success rate and running time. Secondly, a discussion will be held regarding the different solutions available to archive data beyond what is available in HTML source code. Extraction of authors, dates and comments is not part of evaluation because of the lack of publicly available competing projects and reference data sets.

% All experiments are reproducable by following instructions on the \emph{evaluation} branch of the BlogForever-Crawler version control **.
% https://github.com/OlivierBlanvillain/blogforever-crawler-publication

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate post article and title extraction we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}. These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}).

Table \ref{precisionTable} shows extraction success rates for article and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}. An extraction was considered successful when the returned string is a least 0.5 similar to the reference string, with respect to the Sørensen–Dice coefficient similarity. \TODO{fix 0.5...}

@@

On our test-set Algorithm~\ref{extractionAlgo} outperformed the concurrence by 4.9\% on article extraction and 10.1\% on title extraction. It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web pages. Contrariwise, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages. Therefore, results showed in table \ref{precisionTable} should not be interpreted as general quality evaluation of the different projects, but simply show that our approach is more suitable when working with blogs.

@@

% setup
Our measurements were made with garbage collector disabled on an otherwise idle core of an \emph{Intel Core i7-3770 3.4 GHz} processor. Experimental data was obtained by taking the median of 11 mesurements. On this setup we obtained very low standard deviations on the order of 2 milliseconds which are therefor

\TODO{make a paragraph with linux, python and processor}

confidence intervals .. in .. as (max 2ms)

Figure 2 shows the cumulated time spent on each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of process blog posts on the \surl{http://quantumdiaries.org/} website.

% result (plot)
\input{runningtimeFigure.tex}

% discussion: again, we are "cheating" on scalability

% discussion: raw perf (15 feed entry),
% discussion: (c++ vs java vs scala vs go \cite{hundt2011})Implemented in Javascript, Java and Scala respectively
% YUNO algo 2

>>>>

Our evaluation will be articulated in two parts. Firstly, we will compare the article extraction procedure presented in \autoref{algorithms} with three open source projects capable of extracting content and title of web articles. The comparison will show that our blog targeted solution has better performances both in term of success rate and running time. Secondly, a discussion will be held regarding the different solutions available to archive data beyond what is available in HTML source code. Extraction of authors, dates and comments is not part of evaluation because of the lack of publicly available competing projects and reference data sets.

Experiments were made on \emph{Debian GNU/Linux 7.2} with \emph{Python 2.7} on an \emph{Intel Core i7-3770 3.4 GHz} processor. Timing measurements used a single otherwise idle core with garbage collector disabled. The Git repository of this paper \cite{blogforever-crawler-publication} \TODO{cite blogforever-crawler-publication} contains the necessary scripts and instructions to reproduce all evaluation experiments presented in this section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate post article and title extraction we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}, implemented in JavaScript, Java and Scala respectively. These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}). \autoref{precisionTable} shows extraction success rates for article and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}.

% An extraction was considered successful when the returned string is a least 0.5 similar to the reference string, with respect to the Sørensen–Dice coefficient similarity.

@@

On our test-set \autoref{extractionAlgo} outperformed the concurrence by 4.9\% on article extraction and 10.1\% on title extraction. It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web pages. Contrariwise, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages. Therefore, results showed in \autoref{precisionTable} should not be interpreted as general quality evaluation of the different projects, but simply show that our approach is more suitable when working with blogs.

@@

% setup
Experimental data was obtained by taking the arithmetic mean over 10 measurements, which we believe to be significant given that each result has a standard deviations on the order of 2 milliseconds. \comment{Do I have to justify the arithmetic mean? If yes, this could do: \surl{http://dl.acm.org/citation.cfm?id=5673}}

\autoref{runningtime} shows the cumulated time spent on each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed of \surl{http://quantumdiaries.org/}.

\input{runningtimeFigure.tex}

Past the initial computations, the cost to extract an article with our approach are almost null. This is a consequence of having a blog aware, rule based algorithm. If you recall the procedure presented in \autoref{algorithms}, the central idea was to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog. On this example, time cost of parsing a new blog post and using extraction rules is in the order of 3 milliseconds, which is not visible on the scale of \autoref{runningtime}. The three other evaluated solutions do not function this way: each blog post is processed as a new and independent input, leading to a close to linear running times.

In \autoref{runningtime}, the vertical dashed line at 15 processed blog posts represents a suitable point of comparisons for processing time per blog posts. Indeed, as the test blog's web feed contains 15 entries, the time spent on processing the first blog post also includes the processing time of the web feed and it's 15 entries. \comment{Is this clear?}That being said, comparing raw performances of different algorithm implemented with different programming languages is not very informative given the high variations of running times observes across languages for identical algorithms \cite{hundt2011}.

% python x23 just-in-time compilation speed up http://dl.acm.org/citation.cfm?id=2069181

### 2013-12-06 tex/6-conclusion-and-future-work.tex
Add a few ideas from reading the WebDataExtraction,ApplicationsAndTechniques survey, add sripts to run and score theextraction methods.
up

\section{Conclusion and Future Work}
\begin{itemize}
  \item Recap the problem and the objective
  \item Summarize how've solved it
  \item Mention challenges and problems
  \item Hint for future work
\end{itemize}

>>>>

\section{Conclusion and Future Work}
% What we presented, what we solved
In this paper, we presented the internals of the BlogForever web crawler. Its central article extraction procedure based on extraction rules generation was introduced along with theoretical and empirical evidences validating the approach. Simple adaptation of this procedure allowed to extract different types of contents, including authors, dates and comments. In order to support

blogs with JavaScript generated content

We also discussed the overall software architecture, highlighting the design choices made to achieve both modularity and scalability.

% Future work

Plan:
\begin{enumerate}
  \item Recap the problem and the objective
  \item Summarize how've solved it
  \item Mention challenges and problems
  \item Hint for future work
\end{enumerate}

Content:
\begin{enumerate}
  \item Web pages dynamically generated after filling a web form/doing some user action. This is not automated atm.
  \item Spacial reasoning (we already have the page rendered w PhantomJS)
  \item Low level PhantomJS hooks
  \item Tree edit distance matching
\end{enumerate}
